Operation Manual

### 2024-10-29 docs/writing/outline.tex
Adding rough references

		\item tree rings provide critical data/insights across multiple fields
		\item tree rings can help reconstruct past climates 
		\item understanding tree growth mechanisms (plant bio/ecology)

>>>>

		\item tree rings provide critical data/insights across multiple fields % Guibal and Guiot
		\item tree rings can help reconstruct past climates (dendroclimatology) % Sheppard
		\item understanding tree growth mechanisms (plant bio/ecology) % Fritts and Swetnam 
